A performance comparison of Dask and Apache Spark for data-intensive neuroimaging pipelines

### 2019-09-26 latex/paper.tex
Positioned figures
Added figure number to GIL paragraph

\begin{figure}[!b]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/histo_worker.png}%
        \caption{Histogram (Python) makespan}\label{fig:histo_ms_worker}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/histo_idle_worker.png}%
        \caption{Histogram (Python) total time}\label{fig:histo_tt_worker}
    \end{subfigure}
    \caption{125 blocks, 8 CPUs/worker}
\end{figure}

@@

\begin{figure}[!t]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/histo_block.png}%
        \caption{Histogram (Python) makespan}\label{fig:histo_ms_block}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/histo_idle_block.png}%
        \caption{Histogram (Python) total time}\label{fig:histo_tt_block}
    \end{subfigure}
    \caption{8 workers, 8 CPUs/worker}
\end{figure}
% \TG{We decided to omit Dask Futures as it does not have any value over Dask
% Delayed in this application.}

@@

\begin{figure}[!t]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \href{https://mathdugre.github.io/paper-big-data-engines/spark-histo-baseline.html}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/spark_histo_gantt.png}}
        \caption{Spark}\label{fig:histo_spark_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \href{https://mathdugre.github.io/paper-big-data-engines/dask-bag-histo-baseline.html}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/bag_histo_gantt.png}}
        \caption{Dask Bag}\label{fig:histo_dask_bag_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \href{https://mathdugre.github.io/paper-big-data-engines/dask-delayed-histo-baseline.html}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/delayed_histo_gantt.png}}
        \caption{Dask Delayed}\label{fig:histo_dask_delayed_gantt}
    \end{subfigure}
    \caption{Histogram (Python) Gantt chart: 125 blocks, 8 workers, 8
    CPUs/worker}\label{fig:histo_gantt}
\end{figure}

@@

\begin{figure}[!b]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/histo_np_worker.png}%
        \caption{Histogram (NumPy) makespan}\label{fig:histo_np_ms_worker}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/histo_idle_np_worker.png}%
        \caption{Histogram (NumPy) total time}\label{fig:histo_np_tt_worker}
    \end{subfigure}
    \caption{125 blocks, 8 CPUs/worker}
\end{figure}

@@

\begin{figure}[!t]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/histo_np_block.png}%
        \caption{Histogram (NumPy) makespan}\label{fig:histo_np_ms_block}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/histo_idle_np_block.png}%
        \caption{Histogram (NumPy) total time}\label{fig:histo_np_tt_block}
    \end{subfigure}
    \caption{8 workers, 8 CPUs/worker}
\end{figure}

@@

Although Dask reduces the impact of Python's GIL on parallelism by using external
Python extensions, our Python histogram experiment (Figure
~\ref{fig:histo_tt_worker}) showed that issues remain in Dask to
parallelize Python functions. However, Dask was easily able to parallelize
the same application when implemented with Numpy
(Figure~\ref{fig:histo_np_tt_worker}) because in this case the computation
happened in C, outside of the GIL. Similarly, the computation in
command-line applications happens in a sub-process, hence outside of the
GIL, which explains why the BIDS apps example application was not impacted
by this issue. Although implemented in Python, Incrementation was not
impacted either, as computation was only emulated through sleep time.

>>>>

\begin{figure}[!b]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/histo_worker.png}%
        \caption{Histogram (Python) makespan}\label{fig:histo_ms_worker}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/histo_idle_worker.png}%
        \caption{Histogram (Python) total time}\label{fig:histo_tt_worker}
    \end{subfigure}
    \caption{125 blocks, 8 CPUs/worker}\label{fig:histo_worker}
\end{figure}

@@

\begin{figure}[!b]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/histo_block.png}%
        \caption{Histogram (Python) makespan}\label{fig:histo_ms_block}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/histo_idle_block.png}%
        \caption{Histogram (Python) total time}\label{fig:histo_tt_block}
    \end{subfigure}
    \caption{8 workers, 8 CPUs/worker}\label{fig:histo_block}
\end{figure}
% \TG{We decided to omit Dask Futures as it does not have any value over Dask
% Delayed in this application.}

@@

\begin{figure}[!b]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \href{https://mathdugre.github.io/paper-big-data-engines/spark-histo-baseline.html}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/spark_histo_gantt.png}}
        \caption{Spark}\label{fig:histo_spark_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \href{https://mathdugre.github.io/paper-big-data-engines/dask-bag-histo-baseline.html}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/bag_histo_gantt.png}}
        \caption{Dask Bag}\label{fig:histo_dask_bag_gantt}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \href{https://mathdugre.github.io/paper-big-data-engines/dask-delayed-histo-baseline.html}{
        \includegraphics[clip,width=\columnwidth,
        height=0.15\textheight]{images/delayed_histo_gantt.png}}
        \caption{Dask Delayed}\label{fig:histo_dask_delayed_gantt}
    \end{subfigure}
    \caption{Histogram (Python) Gantt chart: 125 blocks, 8 workers, 8
    CPUs/worker}\label{fig:histo_gantt}
\end{figure}

@@

\begin{figure}[!t]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/histo_np_worker.png}%
        \caption{Histogram (NumPy) makespan}\label{fig:histo_np_ms_worker}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/histo_idle_np_worker.png}%
        \caption{Histogram (NumPy) total time}\label{fig:histo_np_tt_worker}
    \end{subfigure}
    \caption{125 blocks, 8 CPUs/worker}\label{fig:histo_np_worker}
\end{figure}

@@

\begin{figure}[!t]
    \centering
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/histo_np_block.png}%
        \caption{Histogram (NumPy) makespan}\label{fig:histo_np_ms_block}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{\columnwidth}
        \includegraphics[clip,width=\columnwidth]{images/histo_idle_np_block.png}%
        \caption{Histogram (NumPy) total time}\label{fig:histo_np_tt_block}
    \end{subfigure}
    \caption{8 workers, 8 CPUs/worker}\label{fig:histo_np_block}
\end{figure}

@@

Although Dask reduces the impact of Python's GIL on parallelism by using external
Python extensions, our Python histogram experiment (Figure
~\ref{fig:histo_worker} and \ref{fig:histo_block}) showed that issues remain in Dask to
parallelize Python functions. However, Dask was easily able to parallelize
the same application when implemented with Numpy
(Figure~\ref{fig:histo_np_worker} and \ref{fig:histo_np_block}) because in this case the computation
happened in C, outside of the GIL. Similarly, the computation in
command-line applications happens in a sub-process, hence outside of the
GIL, which explains why the BIDS apps example application was not impacted
by this issue. Although implemented in Python, Incrementation was not
impacted either, as computation was only emulated through sleep time.
